TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-12-14 paper/paper.tex
paper: minor improvements

@@

During this research a performance test of various TCP congestion algorithms will be performed. The most common TCP congestion algorithms will be determined through desk research. The tests will be conducted in a private environment. Based on the results of those tests, recommendations will be given related to the measures a datacenter has to take to keep the traffic equally allocated over customers.

@@

TODO: Type some text here.

@@

CTCP is the only algorithm that responds excessively to others. Alone, it
reaches the full gigabit speed; but once any other algorithm runs at the same
time (i.e. a normal test is performed), CTCP's speed consistently drops. It
then reaches around 55 megabits ($\pm$5), while the other algorithms reach at %TODO: check 55+-5
least 800 with good network conditions (8 milliseconds latency, 0\% loss).

\begin{figure}[H]
	\centering
		\includegraphics[scale=0.4]{figs/ctcp-bic-8-0.png}
		\caption{TODO}
	\label{fig:packet-loss-chart}
\end{figure}

@@

>>>>

TODO in the next section blah, then blah, and finally blah.

@@

During this research, performance comparison tests of various TCP congestion algorithms will be performed. The most common TCP congestion algorithms will be determined through desk research. The tests will be conducted in an isolated environment. Based on the results of those tests, recommendations will be given related to the measures a datacenter has to take to keep the traffic equally allocated over customers.

@@

In this section we will first elaborate on which algorithms we looked into, next we look at their internal workings, and finally we show the results of our experiments.

@@

CTCP is the only algorithm that responds excessively to others. Alone, it
reaches the full gigabit speed; but if any other algorithm runs at the same
time (i.e. a normal test is performed), CTCP's speed consistently drops. It
then reaches around 55 megabits ($\pm$5), while the other algorithms reach at %TODO: check 55+-5
least 800 with good network conditions (8 milliseconds latency, 0\% loss).
See figure \ref{fig:ctcp-1} for an example of BIC vs. CTCP.

\begin{figure}[H]
	\centering
		\includegraphics[scale=0.4]{figs/ctcp-bic-8-0.png}
		\caption{CTCP vs. BIC with 8ms latency and 0\% loss}
	\label{fig:ctcp-1}
\end{figure}

@@

The full set of results is available online\cite{git-lsproj}.
